Project 2

### 2015-03-31 project2/paper/main.tex
Fleshing out the data section even more

\subsection{Query Results}

>>>>

\subsection{Query Results}
A script was built to call the WMATA API for train estimates, and was setup as a cron job on server. The script
essentially downloaded the estimates of train arrivals for every station into a single timestamped JSON file (see the
JSON format \cite{json}. Cron \cite{crontab} was configured to run the script every minute for an entire week,
resulting in a directory full of timestamped JSON files. These were then imported into a Mongo \cite{mongodb} database 
to allow easier queries.

Train interarrivals were measured by line and direction. \ref{fig:eastboundblueinterarrivals} demonstrates a case where
the data appears to be normal. However, other cases such as \ref{fig:westboundsilverinterarrivals} show that this is
not necessarily true. Graphs for the remaining directions and line colors were omitted for brevity, but are included in
the submission. Due to time constraints, we'll use an empirical distribution rather than trying to fit anything.

\begin{figure}
\begin{center}
\includegraphics[width=4in]{../images/train_interarrivals/eastbound_blue_interarrivals.png}
\caption{\small \sl Eastbound Blue Line Interarrivals at Rosslyn \label{fig:eastboundblueinterarrivals}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=4in]{../images/train_interarrivals/westbound_silver_interarrivals.png}
\caption{\small \sl Westbound Silver Line Interarrivals at Stadium Armory \label{fig:westboundsilverinterarrivals}}
\end{center}
\end{figure}
